Constraining Quiescent Supermassive Black Hole Environments.

### 2014-09-15 ms.tex
Some changes in wording and small modification for figures

We find there is a trend of $\eddr$ increasing towards higher black
hole masses. However, previous work suggests a downsizing trend: for
quiescent galaxies $L_X \sim \Mbh^\alpha$, where $\alpha\simeq
0.7-0.8$ \citep{MillerGallo+:2014a}. If $L_X\sim\dot{M}^2$, this would
suggest $\eddr\sim \Mbh^{-0.6}$. In contrast for fixed $\vwO$ and
$\eta$ we obtain that $\eddr\sim \Mbh^{0.5-1}$. One possible solution
is that $\eta$ decreases with $\Mbh$. $\dot{M}$ scales linearly with
$\eta$, so we would need to have $\eta\sim \Mbh^{-1}$ to explain the
observed downsizing trend.

>>>>

We find there is a trend of $\eddr$ increasing towards higher black
hole masses. However, previous work suggests a downsizing trend: for
quiescent galaxies $L_X \sim \Mbh^\alpha$, where $\alpha\simeq
0.7-0.8$ \citep{MillerGallo+:2014a}. In our model we have $\Mdot \sim
\Mbh^{1.5-2}$. If $L_x\sim M$, then we would have $\L_x \sim
\Mbh^{1.5-2}$, steeper than the observed relationship. (If $L_x \sim
\Mdot^2$ the discrepance becomes worse).  One possible solution • is
that $\eta$ decreases with $\Mbh$.  $\Mdot$ scales linearly with
$\eta$, so we would need to have $\eta \sim \Mbh^{-1}$ to explain the
observed downsizing trend.
